{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2020-11-25 documents/background.tex
words

{\Large {This has \textbf{nothing to do} with 5G communications. }}\\

@@

In fact, it seems like at some point in the 1970, a selective effect on viruses was discovered and progressed as far as a clinical trial. The only record we have of this trial are two citations regarding a conference paper submitted to a New York Academy of Sciences symposium in a 1981 index. This symposium is not listed in Transactions of. The National Institutes of Health may have a copy.

we appear to have lost confidence in the concept of measurement itself.

@@

@@

In inevitable temperature rise as a confounding factor. Power dissipation necessarily produces a  As anyone who has scalded their mouths on microwaved dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.

>>>>

{\Large {This has \textbf{nothing to do} with 5G communications.}}\\

@@

we appear to have lost confidence in the concept of accurate measurement itself.

@@

So far as we are aware, there are no fundamental physical obstacles to non-thermal effects in biological systems. As an example, electroporation is a well-established - now a common laboratory procedure, in which an enormous electric field causes ions in solution to migrate across the membrane,

However, there equally appear to be no fundamental reasons why some small-molecule drug could not bind to the wrong receptor, why

@@

A previous report of microwave resonance, Grundler \cite{Sharp1983}, use a calorimeter, a stream of cooling water controlled to within 0.1 C, an interferometric thermometer, and can state definitively that at no point does the temperature inhomogeneity exceed 0.02 C.

The experiments of the Sun group

An electric field necessarily dissipates energy in the surrounding solvent, and

In inevitable temperature rise as a confounding factor.

As any researchers who have scalded their mouths on microwaved dinner may know, microwave irradiation can produce unintuitive temperature gradients, with local hot-spots that can be difficult to measure directly.

Kozempel \cite{Preliminary1997} and \cite{Inactivationa}. They take great pains to map the temperature profile using a fiber-optic thermometer; use thermographic indicators; and find substantial, almost complete inactivation of {\it Pediococcus sp.} with a measured discharge temperature of only 40 C.

This is a fascinating result, and one which should be compared to the existing literature and very carefully replicated to isolate the mechanism. However, unless it is suggested that {\it Pediococcus sp.} also exhibits a confined microwave resonance of the same nature, it appears that periodic temperature measurements within the physiological range are not necessarily a sufficiently stringent control to definitively isolate resonant effects from other mechanisms.

Conversely, if temperature control is not possible,

In Gandhi \cite{Basic1983}, nichrome heaters and copper-constantan thermocouples are used to generate the same temperature-time profile in both the treatment and the control to within 0.02 C, finding no effect.

Burton\cite{Effects1950} describe the use of thermochromic pigments to examine heating profiles. Using low-frequency exposure, they are able to produce localized regions in excess of 50 C.
